Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-10 paper/main.tex
Udpates

\subsection{Model Testing Using CI Tests}
Our structure learning algorithm relies on suggesting modifications to the
expert based on CI testing. In this section, we show an example of how this
works. Our structure learning algorithm can be thought of an iterative
application of this model testing approach.

>>>>

\subsection{Model Testing Using CI Tests}
Our structure learning algorithm relies on the idea of testing DAGs using CI
tests. In this section, we give an example of how this model testing and
corresponding modification work. We take the example of the MEC learned by the
PC algorithm in Figure~\ref{fig:intro}(b) using $ N=800 $. We first orient all
the undirected edges in the model based on our domain knowledge. In this case
we only have one undirected edge between Marital Status and Relationship. Let's 
orient the edge as Marital Status to Relationship.

 The implied CIs of the 
model along with the test results are shown in Figure.
